An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-06 Paper.tex
Remove custom section-header style
This commit changes the styling of the section labels back to the default style.
Correct and edit proof of normality for oos bootstrap components
Updates Lemma A2, a proof that the individual components of the OOS average
obey a CLT under the bootstrap-induced distribution.  This change corrects some
errors in the original proof and updates the proof strategy to be consistent
with the method proposed in the underlying stationary bootstrap paper (Calhoun
2011).

\begin{lema}\label{res:a3}
  Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
  (f_{t}' - \E f_{t}', a_t h_{t}')'$, $\psi_t^{*} =
  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})', a_t
  h_t^{*\prime})'$, and $a_t = \sum_{s=\max(R,t)}^T \tfrac{1}{s}$.  Then
  \begin{equation}\label{eq:1}
    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}
    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}
    \leq x \Big] \Big| > \epsilon \Big] \to 0
  \end{equation}
  for all positive $\epsilon$.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a3}]
  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}, and
  so it suffices to prove that the bootstrap average obeys a \clt\ as
  well.

  Suppose that $\psi_t^{**}$ is generated by the stationary bootstrap but
  with exactly $\lfloor p P \rfloor$ full blocks of length
  $M_1,\dots,M_{\lfloor p P \rfloor}$ (so that the number of
  observations $P^{**}$ is random).  As in \citet{Cal:11d}, $\sqrt{P}
  \bar{\psi}^{*}$ and $\sqrt{P^{**}} \bar{\psi}^{**}$ converge in
  distribution to the same limit; moreover, $P^{**} \bar{\psi}^{**}$ is a
  sum of $\lfloor p P \rfloor$ independent blocks that obey a central
  limit theorem conditional on $\mathcal{M} = (M_1,\dots,M_{\lfloor p
    P \rfloor}$), and the result follows if $P^{**}
  \E^{**}(\bar{\psi}^{**} \bar{\psi}^{**\prime} \mid \mathcal{M}) \to^p
  \Sigma$ where $\Sigma = P \E(\bar{\psi} \bar{\psi}')$.

  For $\tau = 1,\dots,P^{**}$, let $\kappa$ denote the block
  containing $\tau$, so $\sum_{i=1}^{\kappa-1} M_i < \tau \leq
  \sum_{i=1}^{\kappa} M_i$, and let $K_{\tau,i} = \sum_{j=\kappa+1}^i
  M_{(j \mod \lfloor p P \rfloor) + 1}$, $K_{\tau,0} = 0$.  Then we have
  \begin{multline}
    P^{**} \E^{**}(\bar{\psi}^{**} \bar{\psi}^{**\prime} \mid \mathcal{M})
    = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor} 
    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \hat{\psi}_s \hat{\psi}_t' 
    \\ = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}
    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \big[\psi_s \psi_t' + \psi_s(\hat{\psi}_t
    - \psi_{t})' + (\hat{\psi}_s - \psi_{s}) \psi_{t}' + (\hat{\psi}_s -
    \psi_{s})(\hat{\psi}_t - \psi_{t}) \big],
  \end{multline}
  with the first equality from \citet{Cal:11d} and $\hat{\psi}_s =
  (f_t(\hat{\beta}_{T+1})' - \bar f(\hat{\beta}_{T+1})', h_t')'$.
  Now, $\frac{1}{P^{**}} \sum_i \sum_{s,t} \psi_s \psi_t \to^p \var(\sqrt{P} \bar{\psi})$
  \citep[Lemma~5]{Cal:11d}, so it suffices to show that the remaining
  terms vanish, which is equivalent to showing
  \begin{equation}\label{eq:3}
    \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}\sum_{s,t =
      K_{\tau,i-1}}^{K_{\tau,i}} (f_s(\hat{\beta}_{T+1}) -
    f_s(\beta_0)) (f_t(\hat{\beta}_{T+1}) - f_t(\beta_0))
    \to^p 0
  \end{equation}
  and
  \begin{equation}\label{eq:2}
    (\bar{f}(\hat{\beta}_{T+1}) - \E
    \bar{f}(\beta_0)) (\bar{f}(\hat{\beta}_{T+1}) - \E
    \bar{f}(\beta_0))' \to^p 0.
  \end{equation}
  Proving~\eqref{eq:3} uses the same argument as~\citet[Lemma
  A.3]{Mcc:00} and~\eqref{eq:2} follows a streamlined version of the
  argument of~\ref{res:a5}, completing the proof.  The proofs for the
  moving and circular block bootstraps are the same.
\end{proof}

>>>>

\begin{lema}\label{res:a3}
  Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
  (f_{t}' - \E f_{t}', a_t h_{t}')'$ and $\psi_t^{*} =
  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})',
  h_t^{*\prime})'$.  Then
  \begin{equation}\label{eq:1}
    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}
    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}
    \leq x \Big] \Big| > \epsilon \Big] \to 0
  \end{equation}
  for all positive $\epsilon$.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a3}]
  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}; the
  bootstrap average obeys a \clt\ as well from
  \citet[Theorem~2]{Cal:11d} and is asymptotically normal, so it
  suffices to prove that
  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big) -
  \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t \Big) \to^p 0. \]
  I will prove this result for the Moving Blocks Bootstrap---the proof
  for other block bootstraps is similar and follows as in
  \cite{Cal:11d}.

  \newcommand{\su}{\tfrac{ 1 }{ T - b } \sum_{ \tau = 0 }^{ T - b - 1
    } \tfrac{ 1 }{ b }\sum_{ s, t = \tau + 1 }^{ \tau + b }}

  Note that
  \begin{equation*}
  \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big)
  = \su \hat\psi_s \hat\psi_t'
     - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
  \end{equation*}
  where
  \begin{equation*}
    \tilde \psi( \hat \beta_T
    = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b \tfrac{ t }{ b }
         \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big)
  \end{equation*}
  Since $\bar \psi( \hat \beta_T ) = 0$ by construction and (finish explanation), we have
  \begin{align*}
    \tilde \psi( \hat \beta_T )
    &= \tfrac{ b }{ T } \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b 
       \Big( \tfrac{ t - b }{ b } - \tfrac{ b }{ T } \Big)
       \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big) \\
    &= o_p(1).
  \end{align*}
  Moreover,
  \begin{equation*}
    \su \hat\psi_s \hat\psi_t' \to^p \var \Big( \sum_{t=R+1}^T \psi_t \Big)
  \end{equation*}
  by (de Jong and Davidson reference), completing the proof.
\end{proof}
